% !TEX root = ..\main.tex
\centeredchapterstyle
\begin{abstract}
    \noindent\textbf{Contextualization}: The impact of technology on life in general has been expanding every day, the knowledge in the area has become something of paramount importance for the population in a way that Majority. In this way, disseminating information about technology can, in addition to informing, result in changes in the quality of life, in the development of new technologies among others. other.  \textbf{Objetive}: The focus of the developed website is that anyone with access to to the internet to obtain information about the area of technology, whether for beginners who are building their careers and seeking basic knowledge, as well as for those who are looking to learn about technological innovations or discover new ways to Use any and all types of tools. \textbf{Method}: We seek to implement the studies acquired during the course, as well as knowledge from external research, who were able to help us with the foundation of the project. In the organization, we apply notions absorbed in the methodology subjects, in which we learned how to Optimize every step of the process. In addition, in development, we work with the contents of the current semester. \textbf{Results}: As a result, we sought to develop a website that can spread knowledge and that has articles on various segments, also, that people can share content and that they align with the idea to enhance readers' learning. As well, we also aim to have profitability with the project, whether through access, how to offer space for advertisers and partners who want to be part of the idea of democratizing knowledge
\end{abstract}